A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-10-13 05_calibration_data.Rmd
minor changes

Here we use a speed threshold of 25.6 m/s, a little lower than the 95th percentile.

@@

# filter for boating segment
# data_recurse <- atl_filter_covariates(data = data_recurse,
#  filters = c("between(UTCtime, '2020-08-24 11:13:00', '2020-08-24 12:36:11')"))

>>>>

Here we use a speed threshold of 15 m/s, the fastest known boat speed.

@@
